---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tinycc

[![Travis-CI Build Status](https://travis-ci.org/ottlngr/tinycc.svg?branch=master)](https://travis-ci.org/ottlngr/tinycc) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ottlngr/tinycc?branch=master&svg=true)](https://ci.appveyor.com/project/ottlngr/tinycc) [![Coverage status](https://codecov.io/gh/ottlngr/tinycc/branch/master/graph/badge.svg)](https://codecov.io/github/ottlngr/tinycc?branch=master)

Use the tiny.cc API to shorten URLs!

## API Key

You will need to use an API Key in order to access the tiny.cc API. You will receive an API Key after signing up at tiny.cc.

## Rate Limiting

> Development requests are limited to 50 per day, and no more than 5 concurrent requests from a single IP address at a time.

## API Methods

+ `shorten`
+ `shorten with custum hash`
+ `expand`
+ `expand_batch`
+ `total_visits`
+ `total_visits_batch`
+ `edit` (not implemented in `tinycc`, yet)
+ `delete`
+ `get_requests_count`

## Examples

### Sign up and store credentials

```{r example,eval=FALSE}

# After creating an account at https://tiny.cc/, you can store your credentials using auth()
library(tinycc)

auth("your_login", "your_api_key")
```

### Use the API

```{r}
library(tinycc)

hash <- paste0(sample(c(LETTERS, letters, 0:9), 6, TRUE), collapse = "")
hash

# shorten https://ropensci.org/

shorten(longURL = "https://ropensci.org/", shortURL = hash)
```

## See also

[https://tiny.cc/api-docs]()
